\documentclass[12pt]{article}

\usepackage{parskip}

\title{Leela: Orphan of the Stars}
\author{Philip J. Fry}

\begin{document}
\maketitle

\section*{Act 1}

\subsection*{SCENE 1}

\subsubsection*{WHEREIN LEELA IS FOUND AT THE ORPHANARIUM}

MR VOGEL

Who is this one-eyed female baby Moses?
With courage in her female baby smile.

ORPHANS

A savior from the stars.
Or something stranger still.

BABY LEELA

Or just a lonely filthy starving child!

\subsection*{Scene 2}

\subsubsection*{FIGHT WITH GODZILLA}

BENDER

Leela. Leela. Leela, save him.
Save Fry. Save Fry.
Godzilla will devour him.
As for me, I must be off
to have my doctor check this cough.
[cough] Goodbye.

\section*{Act 2}

\subsection*{Scene 1}

\subsubsection*{IN ROBOT HELL}

FRY

To win Leela's heart
with the Holophonor's art,
I need hands of transcendental quickness.

ROBOT DEVIL

Well, I don't see any danger
in gambling with a stranger.
For my head is of a most amazing thickness.
I'm stupid, I'm stupid
I'm stupider than you.
I'm stupider than you in every way.

\subsection*{Scene 2}

\subsubsection*{ON STAGE [unscripted]}

REAL ROBOT DEVIL

I want my hands back!

REAL FRY

Never!
A deal's a deal!
Even with a dirty dealer!

REAL ROBOT DEVIL

Very well.
Then I'll take what I want from Leela!
Leela has promised me her hand.

REAL LEELA

Fry, you do not understand!
I should have revealed I've been deafened by Bender.
The shame. The shame!
But I feared you'd stop writing this musical splendor.
Deception's the curse of my whimsical gender.
He gave me mechanical ears.
Effective though just a bit garish.
In return without shedding a tear, I agreed
that I'd give him my hand!

REAL ROBOT DEVIL

In marriage!

REAL LEELA

What?!

REAL ROBOT DEVIL

You'll give me your hand in marriage!

REAL HERMES

Is this really happening or just being staged?

REAL FARNSWORTH

It can't be real.

REAL AMY

Not if Leela is engaged.

REAL LEELA [to Robot Devil]

That isn't what I meant.
That isn't what I signed!

REAL ROBOT DEVIL

You should have checked the wording in the fine - print.

REAL LEELA [reading contract]

I'll give you my hand-

REAL LEELA AND ROBOT DEVIL

In marriage.

REAL BENDER

The use of words expressing something of the other than the literal intention.
Now that is irony.

REAL ROBOT DEVIL

I will marry her now and confine her to hell.
How droll. How droll!
Where Styx is a river and not just a band.
Though they'll play our reception if all goes as planned.
Unless Fry, you surrender my hands!

REAL FRY

Destiny has cheated me
by forcing me to decide upon
the woman that I idolize
or the hands of of an automaton.
Without these hands I can't complete
the opera that was captivating her.
But if I keep them, and she marries him.
Than he probably won't want me dating her.

REAL FARNSWORTH

I can't believe the devil is so unforgiving!

REAL ZOIDBERG

I can't believe everybody is just ad libbing.

REAL PREACHER BOT

By the powers vested in me by the state of New New York-

REAL FRY [pushes Robot Devil and Preacher Bot away]

No! Stop! Take my hands!
You evil, metal dork!

REAL ROBOT DEVIL [chops Fry's hands off]

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-engine: xetex
%%% TeX-master: t
%%% End:
